### 2016-06-07 sec1_introduction.tex
Need to rewrite Section 4,5
According to Zhang's comments

As can be seen, there are various co-movement patterns requested by different 
applications and it is cumbersome to design a tailored solution for each type. 
As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns. However, we observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which introduce noisy results and unnecessary computations. We name this scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
making the co-moving behavior very loose.
In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.  Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) is able to avoid such an anomaly directly.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is included in \emph{platoon}, \emph{swarm} and \emph{group} results.}
\label{fig:platoon_weakpoint}
\end{figure}

@@

The other issue with existing methods is that they are 
built on top of centralized indexes that are not scalable. 
To the best of our knowledge, the maximum number of trajectories 
ever evaluated is up to hundreds of trajectories. 
In practice, it is rather common to collect at least hundreds of thousands of trajectories 
and their scalability is left unknown. We conduct a theoretical analysis on the worst-case complexity (as listed in Table~\ref{tbl:existing_co_patterns}) as well as an experimental evaluation with a real trajectory database including million-scale points(as shown in Figure~\ref{fig:related_work_scalability}). 
Results show that their performances degrade dramatically as the dataset size scales up. For instances,
performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.5k} to \emph{2.4k}.
It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which may include billion-scale points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ objects}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1.2k$ timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with over 2 million points.}
    \label{fig:related_work_scalability}
\end{figure}

>>>>

As can be seen, there are various co-movement patterns requested by different 
applications and it is cumbersome to design a tailored solution for each type. 
It is notable that \emph{platoon} pattern is able to represent other
patterns by setting appropriate parameters. However, we observe
that such a pattern definition, due to its overly-relaxed temporal constraints,
loses the fine control of a pattern
which leads to noisy results and unnecessary computations. We name this
scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
making the co-moving behavior very weak. In reality, 
such an anomaly is likely induced by the periodic movements of unrelated objects 
such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc. 
In fact, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) 
are able to directly avoid such an anomaly.

%As can be seen, there are various co-movement patterns requested by different 
%applications and it is cumbersome to design a tailored solution for each type. 
%As pointed in \cite{li2015platoon, li2010swarm}, stringent temporal constraints (e.g., global consecutiveness on \emph{flock} and \emph{convoy}) may miss out many interesting patterns. However, we 
%further observe that pattern definitions with overly-relaxed temporal constraints (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) lose the fine control of a pattern which lead to noisy results and unnecessary computations. We name this scenario as \emph{loose-connection} anomaly. To illustrate, as shown in Figure~\ref{fig:platoon_weakpoint}, the two objects $o_1, o_2$ form a \emph{platoon} pattern 
%$\{o_1,o_2:1,2,3,102,103,104\}$. However, the consecutive segments are $98$ timestamps apart, 
%making the co-moving behavior very loose.
%In reality, such an anomaly is likely induced by the periodic movements of unrelated objects 
%such as, vehicles stopping at the same petrol station, animals pausing at the same water source etc.  Interestingly, none of the temporal-relaxed patterns (e.g., \emph{swarm}, \emph{group} and \emph{platoon}) are able to directly avoid such an anomaly.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. The consecutive segment of $o_1$ and $o_2$ are 98 timestamps apart, however, the pattern $\{o_1, o_2: 1,2,3,102,103,104\}$ is valid in \emph{platoon}, \emph{swarm} and \emph{group} results.}
\label{fig:platoon_weakpoint}
\end{figure}

@@

The other issue with existing methods is that they are 
built on top of centralized indexes which face scalability challenges. 
To the best of our knowledge, the maximum number of trajectories
ever evaluated is up to a million data points.
In practice, it is rather common to collect hundreds of millions data points
and the scalabilities of current solutions are left unknown. 
We conduct a theoretical analysis on the worst-case complexity 
(as listed in Table~\ref{tbl:existing_co_patterns}) as well as 
an experimental evaluation with a real trajectory database 
with upto 2.4 million points (as shown in Figure~\ref{fig:related_work_scalability}). 
Results show that their performances degrade dramatically as the dataset scales up. For instances,
the performance of \emph{swarm} drops five times as the number of objects grows from \emph{1k} to \emph{2k}. Similarly,
the performance of \emph{group} drops over seven times as the number of snapshots grows from \emph{1.4k} to \emph{2.4k}.
Therefore, directly applying these patterns on billion-scale real trajectories is impractical.

%It is easy to spot that none of the existing solutions are scalable to handle large-scale trajectories which include near billions of data points.
%In fact, as shown in Table~, the mining of co-movement patterns require high complexity. For instance, the
%complexities of \emph{swarm} and \emph{platoon} are already exponential. 
%Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_O.eps}
		\subcaption{$1k$ objects}
    \label{fig:fig1}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
            \centering
            \includegraphics[width=\textwidth]{rw_perf_T.eps}
         \subcaption{$1.2k$ timestamps}
    \label{fig:fig2}
    \end{subfigure}
    \caption{Performance measures on existing co-movement patterns. A sampled Geolife data set
    is used with up two 2.4 million data points.}
    \label{fig:related_work_scalability}
\end{figure}
